Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-04-28 awipev-CO2.Rmd
Clean up

@@

# Add the flag location: some samples have been collected at the peer. Notes them here.
# Flag 1 = collected on the peer by Niskin and flag 0 = collected in the FB (normal collect)
 # And keep data with flag 0 for FB location
d <- d%>%
  dplyr::mutate(location_flag = ifelse(datetime == "2016-04-21 09:25:00" | datetime == "2016-02-10 14:00:00" | datetime == "2016-02-17 09:20:00" |datetime == "2016-02-24 14:20:00" | datetime == "2016-02-04 09:30:00" |datetime == "2016-01-27 15:00:00" |datetime == "2016-01-13 13:45:00" |datetime == "2016-01-06 14:10:00" |datetime == "2015-12-24 10:45:00" |datetime == "2015-12-30 13:30:00" |datetime == "2018-01-05 15:20:00" |datetime == "2018-02-02 14:35:00"|datetime == "2018-03-02 14:10:00"|datetime == "2019-05-31 11:45:00", 1,0)
  )
d <- d%>%
  dplyr::filter(location_flag== 0)

@@

# Mercury chloride correction (Dickson et al. 2007, SOP3a)
# AT
d$at <- d$at * 1.0002
#CT
d$ct <- d$ct * 1.0002

@@

# add sal_fb + sal_insitu_ctd + temp_fb + temp_insitu_ctd from d_all into d, to use pHinsi
# use the closest time to add them
closest <- which.closest(d$datetime, d_all$datetime) # closest date and time
d$closest_datetime <- d_all$datetime[closest]
# if the closest value is more than 30 min away, then we do not take it
d$closest_datetime[abs(d$datetime - d_all$datetime[closest]) > 30*60] <- NA
# create closest_datetime in d_all (copy of datetime)
d_all$closest_datetime <- d_all$datetime
d <- left_join(d, d_all%>%dplyr::select(c(closest_datetime, sal_fb, temp_fb, temp_mix, temp_insitu_11m, sal_mix )), by="closest_datetime")

# Conversion of spectro pH to insitu mix T°
pH_seafet <- d %>%
  dplyr::filter(!is.na(pH_s_seafet) & !is.na(temp_mix) )
pH_seafet <- pH_seafet %>%
  dplyr::mutate(ph_s_sf_temp_mix = pHinsi(pH=pH_seafet$pH_s_seafet,ALK=pH_seafet$at_mean_interp*1e-6, Tinsi=pH_seafet$temp_mix, Tlab=pH_seafet$temp_s_lab, Pinsi= pH_seafet$depth/10, S=pH_seafet$sal_mix,Pt=0,Sit=0))

@@

## Whole time series
```{r whole time series, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
#SAL FB 
sal_xts <- dplyr::select(d_all, datetime, sal_fb)
sal_xts <- as.xts(sal_xts, order.by = sal_xts$datetime)
dygraph(sal_xts, group = "awipev", main="Salinity FerryBox)", ylab="Salinity") %>%
            dySeries("sal_fb", color = "blue", strokeWidth = 0, label = "sal_fb") %>%
dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
      dyOptions( drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
    dyLegend(show = "follow")   %>%
    dyAxis("y",valueRange = c(30, 37)) %>%
      dyRangeSelector(height = 30, dateWindow= NULL)
#SAL CTD profile
sal_xts <- dplyr::select(d_all, datetime, sal_insitu_ctd_1m, sal_insitu_ctd_3m, sal_insitu_ctd_5m, sal_insitu_ctd_7m, sal_insitu_ctd_9m)
sal_xts <- as.xts(sal_xts, order.by = sal_xts$datetime)
dygraph(sal_xts, group = "awipev", main="Salinity (in situ CTD, all depths)", ylab="Salinity") %>%
dySeries("sal_insitu_ctd_1m", color = RColorBrewer::brewer.pal(5, "Set1")[1], strokeWidth = 0, label = "1m") %>%
dySeries("sal_insitu_ctd_3m", color = RColorBrewer::brewer.pal(5, "Set1")[2], strokeWidth = 0, label = "3m") %>%
dySeries("sal_insitu_ctd_5m", color = RColorBrewer::brewer.pal(5, "Set1")[3], strokeWidth = 0, label = "5m") %>%
dySeries("sal_insitu_ctd_7m", color = RColorBrewer::brewer.pal(5, "Set1")[4], strokeWidth = 0, label = "7m") %>%
dySeries("sal_insitu_ctd_9m", color = RColorBrewer::brewer.pal(5, "Set1")[5], strokeWidth = 0, label = "9m") %>%
      dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
      dyOptions( drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
    dyLegend(show = "follow")   %>%
    dyAxis("y",valueRange = c(30, 37)) %>%
      dyRangeSelector(height = 30, dateWindow= NULL)
# TEMP Ferrybox SBE45
temp_fb_xts <- dplyr::select(d_all, datetime, temp_fb)
temp_fb_xts <- as.xts(temp_fb_xts, order.by = temp_fb_xts$datetime)
dygraph(temp_fb_xts, group = "awipev", main="Temperature (in Ferrybox)", ylab="Temperature") %>%
      dySeries("temp_fb", color = "blue", strokeWidth = 0, label = "temp_fb") %>%
      dyAxis("y", valueRange = c(-2.5, 10)) %>%
      dyLegend(show = "follow")   %>%
      dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
      dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
      dyRangeSelector(height = 30, dateWindow= NULL)
# TEMP insitu SBE38
temp_insitu_xts <- dplyr::select(d_all, datetime, temp_insitu_11m)
temp_insitu_xts <- as.xts(temp_insitu_xts, order.by = temp_insitu_xts$datetime)
dygraph(temp_insitu_xts, group = "awipev", main="Temperature (in situ 11 m)", ylab="Temperature") %>%
      dySeries("temp_insitu_11m", color = "blue", strokeWidth = 0, label = "temp_insitu_11m") %>%
      dyAxis("y", valueRange = c(-2.8, 10)) %>%
      dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
      dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
      dyLegend(show = "follow")   %>%
      dyRangeSelector(height = 30, dateWindow= NULL)
# TEMP insitu CTD
temp_insitu_xts <- dplyr::select(d_all, datetime, temp_insitu_ctd_1m, temp_insitu_ctd_3m, temp_insitu_ctd_5m, temp_insitu_ctd_7m, temp_insitu_ctd_9m)
temp_insitu_xts <- as.xts(temp_insitu_xts, order.by = temp_insitu_xts$datetime)
dygraph(temp_insitu_xts, group = "awipev", main="Temperature (ctd all depths)", ylab="Temperature") %>%
      dySeries("temp_insitu_ctd_1m", color = RColorBrewer::brewer.pal(5, "Set1")[1], strokeWidth = 0, label = "1m") %>%
dySeries("temp_insitu_ctd_3m", color = RColorBrewer::brewer.pal(5, "Set1")[2], strokeWidth = 0, label = "3m") %>%
dySeries("temp_insitu_ctd_5m", color = RColorBrewer::brewer.pal(5, "Set1")[3], strokeWidth = 0, label = "5m") %>%
dySeries("temp_insitu_ctd_7m", color = RColorBrewer::brewer.pal(5, "Set1")[4], strokeWidth = 0, label = "7m") %>%
dySeries("temp_insitu_ctd_9m", color = RColorBrewer::brewer.pal(5, "Set1")[5], strokeWidth = 0, label = "9m") %>%
  dyAxis("y", valueRange = c(-2.8, 10)) %>%
      dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
      dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
      dyLegend(show = "follow")   %>%
      dyRangeSelector(height = 30, dateWindow= NULL)
# PCO2 
#+ Ajout de la pCO2 corrigé par le script contros (dans R server ny-alesund_cc.R)
pco2_contros_xts <- dplyr::select(d_all, datetime, pco2_calc, pco2_corr)
pco2_contros_xts <- as.xts(pco2_contros_xts, order.by = d_all$datetime)
dygraph(pco2_contros_xts, group = "awipev", main="pCO2", ylab="pCO2") %>%
    dySeries("pco2_corr", label="Corrected pCO2", color=  "blue",strokeWidth=0, pointSize=2) %>%
    dySeries("pco2_calc", label="calculated pCO2",color = "red", strokeWidth = 0, pointSize = 4 ) %>%
    dyEvent(as.POSIXct("2016-02-28 12:00:00", tz="GMT"), "CO2FT-0515-001 installed", labelLoc = "bottom", color="red") %>% 
    dyEvent(as.POSIXct("2017-02-07 12:00:00", tz="GMT"), "CO2FT-0215-001 installed", labelLoc = "bottom", color="red") %>%
    dyEvent(as.POSIXct("2018-04-16 12:00:00", tz="GMT"), "CO2FT-0515-001 installed", labelLoc = "bottom", color="red") %>% 
    dyEvent(as.POSIXct("2018-10-31 15:00:00", tz="GMT"), "CO2FT-0215-001 installed", labelLoc = "bottom", color="red") %>% 
    dyEvent(as.POSIXct("2019-09-03 15:00:00", tz="GMT"), "CO2FT-0515-001 installed", labelLoc = "bottom", color="red") %>% 
    #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
    dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE) %>%
    dyLegend(show = "follow")   %>%
    dyRangeSelector(height = 30, dateWindow= NULL)
# # DURAFET 
# durafet_contros_xts <- dplyr::select(d_all, datetime, ph_dur, ph_s_dur_temp_fb)
# durafet_contros_xts <- as.xts(durafet_contros_xts, order.by = d_all$datetime)
# dygraph(durafet_contros_xts, group = "awipev", main="pH durafet (in Ferrybox)", ylab="pHT") %>%
#     dySeries("ph_dur", label = "Raw durafet pH", color ="blue", strokeWidth=0, pointSize=2) %>%
#     dySeries("ph_s_dur_temp_fb", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
#     dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "durafet installed", labelLoc = "bottom", color="red") %>%
#     dyEvent(as.POSIXct("2017-10-30 13:00:00", tz="GMT"), "New holder installed", labelLoc = "bottom", color="red") %>% 
#     # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
#     dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
#     dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
#     dyAxis("y",valueRange = c(8, 8.8)) %>%
#     dyLegend(show = "follow")   %>%
#     dyRangeSelector(height = 30, dateWindow= NULL) 
# # SEAFET 
# seafet_contros_xts <- dplyr::select(d_all, datetime, phINT,ph_s_sf_temp_mix)
# seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
# dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ T CTD)", ylab="pHT") %>%
#   dySeries("phINT", label = "Raw data INT", color ="blue", strokeWidth=0, pointSize=2) %>%
#   dySeries("ph_s_sf_temp_mix", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
#   dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
#   dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>% 
#   dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
#     dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
#     dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
#     dyAxis("y",valueRange = c(7.45, 8.8)) %>%
#     dyLegend(show = "follow")   %>%
#     dyRangeSelector(height = 30, dateWindow= NULL) 
# # TA
# # to create periods according to TA deployments
TAevents <- c("2016-02-26 00:00:00", "2017-02-09 12:00:00", "2017-02-09 12:00:00", "2017-03-10 12:00:00",
              "2018-01-07 00:00:00", "2018-06-20 00:00:00", "2018-07-31 00:00:00", "2018-10-30 18:00:00", "2018-10-31 09:00:00", "2019-01-16 09:00:00", "2019-01-26 13:25:00", format(Sys.Date(), "%Y-%m-%d %H:%M:%S"))

# at_contros_cleaned_xts <- dplyr::select(d_all, datetime,AT,at)
# at_contros_cleaned_xts <-  as.xts(at_contros_cleaned_xts, order.by = d_all$datetime)
# dygraph(at_contros_cleaned_xts, group = "awipev", main=" Total Alkalinity (in Ferrybox)", ylab="Total alkalinity") %>%
#    #dySeries("at_contros", color = RColorBrewer::brewer.pal(3, "Set2"), strokeWidth = 0, pointSize=2) %>%
#   #dySeries("AT_filtered2", color = RColorBrewer::brewer.pal(4, "Set2"), strokeWidth = 0, pointSize=2) %>%
#   dySeries("at", label="TA reference",color = "red", strokeWidth = 0, pointSize=4) %>% 
#   dySeries("AT", label= "Raw TA", color = "blue", strokeWidth = 0, pointSize=2) %>%
#   dyEvent(as.POSIXct("2016-05-31 10:00:00", tz="GMT"), "HCl Changed", labelLoc = "bottom") %>%
#   dyEvent(as.POSIXct("2016-06-24 10:00:00", tz="GMT"), "BCG Changed", labelLoc = "bottom") %>%
#   dyEvent(as.POSIXct("2016-02-24 14:00:00", tz="GMT"), "Calibration 1", labelLoc = "bottom") %>%
#   dyEvent(as.POSIXct("2016-09-16 10:00:00", tz="GMT"), "Calibration 2", labelLoc = "bottom") %>% 
#   dyEvent(as.POSIXct("2017-03-21 12:00:00", tz="GMT"), "TA analyser changed", labelLoc = "top", color="red") %>%
#   dyEvent(as.POSIXct("2018-01-08 12:55:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
#   dyEvent(as.POSIXct("2018-07-31 00:00:00", tz="GMT"), "TA analyser changed #TA-1215-001", labelLoc = "top", color="red") %>%
#   dyEvent(as.POSIXct("2018-10-30 18:00:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
#   dyEvent(as.POSIXct("2016-11-15 09:00:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
#   dyEvent(as.POSIXct("2017-02-09 12:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
#   dyEvent(as.POSIXct("2017-04-11 06:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
#   dyEvent(as.POSIXct("2018-01-22 13:00:12", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
#   dyEvent(as.POSIXct("2018-05-16 12:39:39", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
#   dyEvent(as.POSIXct("2018-10-31 10:29:27", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
#   dyEvent(as.POSIXct("2019-01-26 13:25:20", tz="GMT"), "Calibration mode - CRM", labelLoc = "bottom") %>%
#   #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
#   dyShading(from = TAevents[1], to = TAevents[2], color = "#EDEDED") %>%
#   dyShading(from = TAevents[3], to = TAevents[4], color = "#C2C2C2") %>%
#   dyShading(from = TAevents[5], to = TAevents[6], color = "#EDEDED") %>%
#   dyShading(from = TAevents[7], to = TAevents[8], color = "#C2C2C2") %>%
#   dyShading(from = TAevents[9], to = TAevents[10], color = "#EDEDED") %>%
#   dyShading(from = TAevents[11], to = TAevents[12], color = "#C2C2C2") %>%
#   dyAxis("y",valueRange = c(2000, 2650)) %>%
#   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
#   dyOptions( strokeWidth= 0) %>%
#   dyLegend(show = "follow")   %>%
#   dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE) %>%
#     dyRangeSelector(height = 30, dateWindow= NULL) 
#  
f <- as.data.frame(table(d_all$at))
#sum(f$Freq)  
# Number of outliers removed in the dataset
# numberOutliers <- length(which((dat_ATnoNA$outliers > 0)))

# #plot for POSTER june 2019
# #plot of S/T
# poster_temp <- ggplot(data = d_all%>%dplyr::filter(temp_fb<10 &sal>30 )) + geom_point(aes(x=datetime,y=temp_fb),col="blue", size=0.5) +
#   geom_point(aes(x=datetime,y=sal/5),col="red", size=0.5 )+
#   labs(x = "Time", y="Temperature (°C)") +
#   scale_x_datetime(date_minor_breaks ="1 month")+
#   theme_bw() + theme(legend.position="bottom",legend.title = element_blank())+
#   scale_y_continuous(sec.axis = sec_axis(~.*5, name = "Salinity"))
# print(poster_temp)
# #
# png("figures/poster_sal_temp.png", width= 1100, height=600)
# par(mar=c(5, 4, 4, 6) + 0.1)
# #
# plot(sal ~ datetime,d_all,pch=16, axes=T, ylim=c(30.5,36), cex=0.5, col="red", ylab="", xlab="", yaxt ="n", lty=1, cex.axis=1.8) +
# axis(2, ylim=c(0,1),col="red",col.axis="red", las = 1,lty=1, cex.axis =1.8)
# #
#    grid(lty=1)
# #
#    par(new = T)
# #
# plot(as.Date(d_all$datetime,"%Y-%m-d %H:%M:%S", tz= "UTC"), d_all$temp_fb, col="blue", pch=16, cex=0.5, xlab="", ylab="",xaxt="n", axes=FALSE,ylim=c(-2,9))+
# axis(side = 4, col="blue",col.axis="blue",las=1, cex.axis =1.8) +
# mtext("",side=1,col="black",line=1.5, cex=1.8)
# legend("topleft", legend=c("Temperature (°C)", "Salinity"),
#        col = c("blue", "red"), pch  = c(16, 16),  box.lty=0 , cex = 2)
#   grid(nx = 1, ny = NULL, col = "lightgray", lty = 1,
#     lwd = "months")
#      box()
#      dev.off()
# 
# 
# ggsave(paste0("figures/poster_temp.png"), width= 30, height=10, poster_temp, units="cm")
# #
# poster_sal <- ggplot(data = d_all%>%dplyr::filter(sal>30 ), aes(x=datetime,y=sal), colour="sal") +
#   geom_point(col="blue", size=0.5 )+
#   labs(x = "Time", y="Salinity (PSU)") +
#   scale_x_datetime(date_minor_breaks ="1 month")+
#   theme_bw() + theme(legend.position="bottom",legend.title = element_blank())
# print(poster_sal)
# ggsave(paste0("figures/poster_sal.png"), width= 30, height=10, poster_sal, units="cm")

@@

```{r Sal profile, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
df <- d_all %>% 
  dplyr::select(datetime, sal_insitu_ctd_1m, sal_insitu_ctd_3m, sal_insitu_ctd_5m, sal_insitu_ctd_7m, sal_insitu_ctd_9m) %>%
  dplyr::mutate(date = format(datetime, '%Y-%m-%d')) %>% 
  group_by(date) %>% 
  summarize(mean1m = mean(sal_insitu_ctd_1m, na.rm = TRUE),
            mean9m = mean(sal_insitu_ctd_9m, na.rm = TRUE),
            range = mean(sal_insitu_ctd_1m, na.rm = TRUE)-mean(sal_insitu_ctd_9m, na.rm = TRUE)) %>% 
  ungroup()
summary(df)
```
There are `r sum(!is.na(df$range))` days with salinity values at both 1 m (0-2 m) and 9 m (> 8 m). The salinity difference between 1 and 9 m ranges between `r min(df$range)` and `r max(df$range)` (mean: `r mean(df$range)`; `r median(df$range)`). The difference with depth is therefore significant.

@@

p_sal_fb_ctd<-  ggplot(d_all,aes(x=sal_insitu_ctd_9m, y= sal_fb))+
  geom_point( aes(color=factor(month))) + 
 # scale_color_viridis_d(option = "C", guide="none")+
  #geom_line(aes(x = sal_fb, y = sal_fb), linetype = "dashed") +
  geom_abline(slope=1, intercept=0, linetype = "dashed")+
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  ylim(c(30.5,35.5)) +xlim(c(28,35.5)) +
  labs(title = paste("","\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + #
  coord_fixed(ratio = 1 )+
 #  scale_colour_discrete(guide="none") +
  labs( x="Salinity CTD 9 m", y="Salinity FB ", color = "Months") +theme_bw()

print(p_sal_fb_ctd)

@@

@@

p_temp_11_fb<-  ggplot(d_all,aes(x=temp_insitu_11m, y= temp_fb, label = month))+
  geom_text( aes(color=factor(month))) + 
 # scale_color_viridis_d(option = "C", guide="none")+
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  labs(title = paste("T FB vs T 11 m","\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 )+ scale_colour_discrete(guide="none") +
  labs( x="T 11 m", y="T FB ", color = "Months")  +theme_bw()
print(p_temp_11_fb)

@@

####
## calculation of E0INT25/E0EXT25 ##
##     new sf_calib function      ##
####
calib_spectro <- sf_calib(calEint = d_all$voltINT, calEext = d_all$voltEXT, calpH = d_all$ph_s_sf_temp_mix,
                          calT = d_all$temp_sf, calSal = d_all$sal_insitu_ctd)
# put number of deployment 
calib_spectro$deployment_sf <- d_all$deployment_sf

@@

### **Spectro / seaFET**

>>>>

#################### Function RMSE root mean square error
rmse <- function(error) { sqrt(mean(error^2)) }
#rmse(fit$residuals)

@@

# Add the flag location: some samples have been collected at the pier. Notes them here.
# Flag 1 = collected on the peer by Niskin and flag 0 = collected in the FB (normal collect)
 # And keep data with flag 0 for FB location
d <- d%>%
  dplyr::mutate(location_flag = ifelse(datetime == "2016-04-21 09:25:00" | datetime == "2016-02-10 14:00:00" | datetime == "2016-02-17 09:20:00" |datetime == "2016-02-24 14:20:00" | datetime == "2016-02-04 09:30:00" |datetime == "2016-01-27 15:00:00" |datetime == "2016-01-13 13:45:00" |datetime == "2016-01-06 14:10:00" |datetime == "2015-12-24 10:45:00" |datetime == "2015-12-30 13:30:00" |datetime == "2018-01-05 15:20:00" |datetime == "2018-02-02 14:35:00"|datetime == "2018-03-02 14:10:00"|datetime == "2019-05-31 11:45:00", 1, 0)
  )
d <- d%>%
  dplyr::filter(location_flag== 0)

@@

# Mercuric chloride correction (Dickson et al. 2007, SOP3a)
# AT
d$at <- d$at * 1.0002
#CT
d$ct <- d$ct * 1.0002

@@

# add sal_fb + sal_insitu_ctd + temp_fb + temp_insitu_ctd from d_all into d, to use pHinsi
# use the closest time to add them
closest <- which.closest(d$datetime, d_all$datetime) # closest date and time
d$closest_datetime <- d_all$datetime[closest]
# if the closest value is more than 30 min away, then we do not take it
d$closest_datetime[abs(d$datetime - d_all$datetime[closest]) > 30*60] <- NA
# create closest_datetime in d_all (copy of datetime)
d_all$closest_datetime <- d_all$datetime
d <- left_join(d, d_all%>%dplyr::select(c(closest_datetime, sal_fb, temp_fb, temp_sf, temp_mix, temp_insitu_11m, sal_mix)), by="closest_datetime")

# Conversion of spectro pH to insitu mix T°
pH_seafet <- d %>%
  dplyr::filter(!is.na(pH_s_seafet) & !is.na(temp_sf) )
pH_seafet <- pH_seafet %>%
  dplyr::mutate(ph_s_sf_temp_mix = pHinsi(pH=pH_seafet$pH_s_seafet,ALK=pH_seafet$at_mean_interp*1e-6, Tinsi=pH_seafet$temp_sf, Tlab=pH_seafet$temp_s_lab, Pinsi= pH_seafet$depth/10, S=pH_seafet$sal_mix,Pt=0,Sit=0))

@@

@@

```{r Sal profile, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
sal_xts <- dplyr::select(d_all, datetime, sal_fb)
sal_xts <- as.xts(sal_xts, order.by = sal_xts$datetime)
dygraph(sal_xts, group = "awipev", main="Salinity (in FerryBox)", ylab="Salinity") %>%
            dySeries("sal_fb", color = "blue", strokeWidth = 0, label = "sal_fb") %>%
dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
      dyOptions( drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
    dyLegend(show = "follow")   %>%
    dyAxis("y",valueRange = c(30, 37)) %>%
      dyRangeSelector(height = 30, dateWindow= NULL)
#SAL CTD profile
sal_xts <- dplyr::select(d_all, datetime, sal_insitu_ctd_1m, sal_insitu_ctd_3m, sal_insitu_ctd_5m, sal_insitu_ctd_7m, sal_insitu_ctd_9m)
sal_xts <- as.xts(sal_xts, order.by = sal_xts$datetime)
dygraph(sal_xts, group = "awipev", main="Salinity (in situ CTD, all depths)", ylab="Salinity") %>%
dySeries("sal_insitu_ctd_1m", color = RColorBrewer::brewer.pal(5, "Set1")[1], strokeWidth = 0, label = "1m") %>%
dySeries("sal_insitu_ctd_3m", color = RColorBrewer::brewer.pal(5, "Set1")[2], strokeWidth = 0, label = "3m") %>%
dySeries("sal_insitu_ctd_5m", color = RColorBrewer::brewer.pal(5, "Set1")[3], strokeWidth = 0, label = "5m") %>%
dySeries("sal_insitu_ctd_7m", color = RColorBrewer::brewer.pal(5, "Set1")[4], strokeWidth = 0, label = "7m") %>%
dySeries("sal_insitu_ctd_9m", color = RColorBrewer::brewer.pal(5, "Set1")[5], strokeWidth = 0, label = "9m") %>%
      dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
      dyOptions( drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
    dyLegend(show = "follow")   %>%
    dyAxis("y",valueRange = c(30, 37)) %>%
      dyRangeSelector(height = 30, dateWindow= NULL)

df <- d_all %>% 
  dplyr::select(datetime, sal_insitu_ctd_1m, sal_insitu_ctd_3m, sal_insitu_ctd_5m, sal_insitu_ctd_7m, sal_insitu_ctd_9m) %>%
  dplyr::mutate(date = format(datetime, '%Y-%m-%d')) %>% 
  group_by(date) %>% 
  summarize(mean1m = mean(sal_insitu_ctd_1m, na.rm = TRUE),
            mean9m = mean(sal_insitu_ctd_9m, na.rm = TRUE),
            range = mean(sal_insitu_ctd_1m, na.rm = TRUE)-mean(sal_insitu_ctd_9m, na.rm = TRUE)) %>% 
  ungroup()
```
There are `r sum(!is.na(df$range))` days with salinity values at both 1 m (0-2 m) and 9 m (> 8 m). The salinity difference between 1 and 9 m ranges between `r min(df$range)` and `r max(df$range)` (mean: `r mean(df$range)`; `r median(df$range)`). The difference with depth is therefore significant.

@@

p <-  ggplot(d_all,aes(x=sal_insitu_ctd_9m, y= sal_fb))+
  geom_point( aes(color=factor(month))) + 
 # scale_color_viridis_d(option = "C", guide="none")+
  #geom_line(aes(x = sal_fb, y = sal_fb), linetype = "dashed") +
  geom_abline(slope=1, intercept=0, linetype = "dashed")+
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  ylim(c(30.5,35.5)) +xlim(c(28,35.5)) +
  labs(title = paste("","\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + #
  coord_fixed(ratio = 1 )+
 #  scale_colour_discrete(guide="none") +
  labs( x="Salinity CTD 9 m", y="Salinity FB ", color = "Months") +theme_bw()

print(p) #p_sal_fb_ctd

@@

```{r temperature time series, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
# TEMP Ferrybox SBE45
temp_fb_xts <- dplyr::select(d_all, datetime, temp_fb)
temp_fb_xts <- as.xts(temp_fb_xts, order.by = temp_fb_xts$datetime)
dygraph(temp_fb_xts, group = "awipev", main="Temperature (in Ferrybox)", ylab="Temperature") %>%
      dySeries("temp_fb", color = "blue", strokeWidth = 0, label = "temp_fb") %>%
      dyAxis("y", valueRange = c(-2.5, 10)) %>%
      dyLegend(show = "follow")   %>%
      dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
      dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
      dyRangeSelector(height = 30, dateWindow= NULL)
# TEMP insitu SBE38
temp_insitu_xts <- dplyr::select(d_all, datetime, temp_insitu_11m)
temp_insitu_xts <- as.xts(temp_insitu_xts, order.by = temp_insitu_xts$datetime)
dygraph(temp_insitu_xts, group = "awipev", main="Temperature (in situ 11 m)", ylab="Temperature") %>%
      dySeries("temp_insitu_11m", color = "blue", strokeWidth = 0, label = "temp_insitu_11m") %>%
      dyAxis("y", valueRange = c(-2.8, 10)) %>%
      dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
      dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
      dyLegend(show = "follow")   %>%
      dyRangeSelector(height = 30, dateWindow= NULL)
```

@@

p <-  ggplot(d_all,aes(x=temp_insitu_11m, y= temp_fb, label = month))+
  geom_text( aes(color=factor(month))) + 
 # scale_color_viridis_d(option = "C", guide="none")+
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  labs(title = paste("T FB vs T 11 m","\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 )+ scale_colour_discrete(guide="none") +
  labs( x="T 11 m", y="T FB ", color = "Months")  +theme_bw()
print(p) # p_temp_11_fb

@@

####
## calculation of E0INT25/E0EXT25 ##
##     new sf_calib function      ##
####
calib_spectro <- sf_calib(calEint = d_all$voltINT, calEext = d_all$voltEXT, calpH = d_all$ph_s_sf_temp_mix,
                          calT = d_all$temp_sf, calSal = d_all$sal_mix_interp)
# put number of deployment 
calib_spectro$deployment_sf <- d_all$deployment_sf

@@

<!-- ### **Spectro / seaFET** -->
